---
title: "landsimR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{landsimR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Basic Virtual Landscape Creation:


Create polygon (patch) `landscape` using `create_landscape()`
```{r example, warning=FALSE}
library(landsimR)

set.seed(1)
landscape <- create_landscape(
  dim = c(100, 100),
  f = c(.05, .05, .05),
  q = c(.05, .2, .5)
)

colors <- c('green', 'blue', 'orange', 'yellow', 'black', 'brown')

image(landscape, col = colors[1:4])
```


Add line features to `landscape` with `add_lines()`
```{r add-lines, warning=FALSE}
landscape <- add_lines(
  landscape,
  f = c(1, .025),
  q = c(F, .025),
  overlap = c(2, 3)
)

image(landscape, col = colors)
```


Convert `landscape` to `LandscapeObj` class
```{r LandscapeObj-class}
landscape <- LandscapeObj(
  landscape,
  classType = c(1,1,1,1,2,3)
)

class(landscape)
```


View `LandscapeObj`
```{r LandscapeObj-view}
landscape
```


View the structure of `LandscapeObj` 
```{r LandscapeObj-str}
str(landscape)
```



Use generic `plot()` function for `LandscapeObj`
```{r generic-plot}
plot(landscape, col = colors)
```


## Randomization:


Use parameter randomization to create a random landscape 
```{r random-landscape, warning=FALSE}

seed <- 0
set.seed(seed)

random_parameters <- list(
  poly = list(
  f = c(runif(1, 0.005, .01),
        runif(1, .001, .1),
        runif(1, .005, .05)
        ),
  q = c(runif(1, 0, .1),
        runif(1, 0.05, .25),
        runif(1, 0.5, .9)
        )
  ),
  line = list(
    f = c(1, runif(1, .025, .1)),
    q = c(F, .05)
  )
)

random_landscape <- create_landscape(
  dim = c(100, 100),
  f = random_parameters$poly$f,
  q = random_parameters$poly$q
)

random_landscape <- random_landscape |> 
  add_lines(
    random_parameters$line$f,
    random_parameters$line$q,
    overlap = c(2, 3)
)

image(random_landscape, col = colors)
```


## Parameter estimation:


Estimate the input parameters of the random landscape using `estimate_parameters()` function. The first (pink) class of `estimated_landscape` is leftover cells
```{r estimate-parameters, warning = F}
estimated_parameters <- estimate_parameters(
  landscape = random_landscape,
  curve = 5,
  line = 4
)

# for (i in seq_along(estimated_parameters)){
#   for (j in seq_along(estimated_parameters[[i]])){
#     for (k in seq_along(estimated_parameters[[i]][[j]])){
#       if (estimated_parameters[[i]][[j]][k] < 0) {
#         estimated_parameters[[i]][[j]][k] <- .0001
#       }
#     }
#   }
# }

estimated_landscape <- create_landscape(
  dim = c(100, 100),
  # f = parameters$poly$f[2:4],
  # q = parameters$poly$q[2:4]
  f = estimated_parameters$poly$f,
  q = estimated_parameters$poly$q
) 

estimated_landscape <- estimated_landscape |>
  add_lines(
    f = (estimated_parameters$line$f),
    q = (estimated_parameters$line$q),
    # overlap = c(2, 3)
    overlap = c(3, 4)
)

# par(mfrow = c(1, 2))
# plot(random_landscape, col = c('green', 'blue', 'orange', 'yellow', 'black', 'brown'), axes = F, main = 'sample landscape')

image(estimated_landscape, col = c('pink', colors))
```


Random parameters and estimation
```{r parameter-values, echo=FALSE}
df <- data.frame(
  random = random_parameters |> unlist(),
  estimated = (estimated_parameters |> unlist())[-c(1, 5)]
)

df$difference <- abs(df$random - df$estimated)
df$parameter <- rownames(df)
rownames(df) <- NULL

knitr::kable(
  df[, c(4, 1, 2, 3)],
  align = 'c',
  # format = 'latex',
  # label = 'Parameters:',
  # caption = 'popisek',
  col.names = c('Parameter', 'Random', 'Estimated', 'Difference (abs)')
)
```


Replace the leftover cells with the most common value around the cell
```{r test-chunk, warning=FALSE, message=FALSE}
# library(devtools)
# devtools::load_all('~/landsimR/')

estimated_landscape <- estimated_landscape |>
  .poly_landscape(c(1:max(estimated_landscape)), not = 5)

image(estimated_landscape, col = colors)
```


Side by side comparison of random and estimated
```{r side-by-side}
par(mfrow = c(1, 2))
image(random_landscape, col = colors, main = 'Random')
image(estimated_landscape, col = colors, main = 'Estimated')
```
